% ---------------------------------------------------------------
% ABSTRACT
% ---------------------------------------------------------------
\newpage
\begin{center}
  \textbf{\Huge \underline{Abstract}} \\[1.5cm]
\end{center}

The internship described in this document was undertaken by \textbf{Prajapati Anilkumar Mangilal}
(U22CS136) in the capacity of an Application Engineer at \textbf{IDFC FIRST Bank}, distributed across 
two geographic locations: Hyderabad (January through March 2026) and Chennai (April through June 2026).

The internship program was divided into three distinct components, including comprehensive training, 
a collaborative development project, and an independent engineering contribution.

During the \textbf{initial phase}, participants engaged in intensive DOJO training sessions covering 
GoLang programming, concurrent programming primitives (goroutines and channels), the Gin 
microframework, container technology using Docker, and test-driven methodologies including Driver-Navigator 
and Ping-Pong collaborative coding approaches. This extensive preparation was delivered through 
rigorous in-house educational initiatives.

The \textbf{secondary phase} entailed execution of a comprehensive Agile project environment --- 
\textit{SkyFox Cinemas} --- a ticketing and reservation system for cinema operations developed through 
three sequential one-week Agile iterations by a multidisciplinary cohort of eleven interns. The author 
contributed significantly as \textbf{Tech Lead}. Principal technological accomplishments included the 
construction of a high-concurrency seat reservation system utilizing PostgreSQL transactional locks, 
an application programming interface for managing movie schedules, and versioned data storage upgrades 
using the Goose library within GoLang. Feature development remains underway with reservation cancellation 
and partial check-in capabilities in active development.

The \textbf{principal technical initiative} comprised independent development and design of a 
\textbf{Robust Event Consumption Framework} implemented in GoLang, addressing a significant 
regulatory requirement within the bank's Kafka-based distributed service platform. The framework 
encompasses six integrated subsystems: an exponential backoff retry mechanism with randomization, 
a cache-based deduplication repository, a messaging queue for unprocessable data with alerting capability, 
a command-line recovery application, a metrics collection layer compatible with Prometheus, and a 
configurable environment settings management system --- delivering \textbf{complete data retention} 
during temporary infrastructure disruptions and \textbf{87\% test coverage}, surpassing the bank's 
quality benchmarks.