% ---------------------------------------------------------------
% BIBLIOGRAPHY
% ---------------------------------------------------------------

\begin{thebibliography}{99}

\bibitem{Bernstein2009}
Philip A. Bernstein and Eric Newcomer.
\newblock \textit{Principles of Transaction Processing}.
\newblock 2nd edition. Morgan Kaufmann, 2009.

\bibitem{Hohpe2003}
Gregor Hohpe and Bobby Woolf.
\newblock \textit{Enterprise Integration Patterns: Designing, Building, and
Deploying Messaging Solutions}.
\newblock Addison-Wesley, 2003.

\bibitem{Schwaber2020}
Ken Schwaber and Jeff Sutherland.
\newblock \textit{The Scrum Guide: The Definitive Guide to Scrum --- The Rules
of the Game}.
\newblock Scrum.org, 2020.
\newblock Available at: \url{https://scrumguides.org/scrum-guide.html}

\bibitem{Kreps2011}
Jay Kreps, Neha Narkhede, and Jun Rao.
\newblock Kafka: A distributed messaging system for log processing.
\newblock In \textit{Proceedings of the NetDB Workshop at VLDB}, 2011.
\newblock Available at: \url{https://notes.stephenholiday.com/Kafka.pdf}

\bibitem{Google2016}
Betsy Beyer, Chris Jones, Jennifer Petoff, and Niall Richard Murphy (Eds.).
\newblock \textit{Site Reliability Engineering: How Google Runs Production
Systems}.
\newblock O'Reilly Media, 2016.
\newblock Available at: \url{https://sre.google/sre-book/table-of-contents/}

\bibitem{Prometheus2024}
Prometheus Authors.
\newblock \textit{Prometheus: Open-Source Monitoring and Alerting Toolkit ---
Documentation}.
\newblock 2024.
\newblock Available at: \url{https://prometheus.io/docs/introduction/overview/}
\newblock Accessed: 2026.

\bibitem{Gin2024}
Gin Contributors.
\newblock \textit{Gin Web Framework --- Official Documentation}.
\newblock 2024.
\newblock Available at: \url{https://gin-gonic.com/docs/}
\newblock Accessed: 2026.

\bibitem{GoDoc2024}
The Go Authors.
\newblock \textit{The Go Programming Language --- Official Documentation}.
\newblock 2024.
\newblock Available at: \url{https://go.dev/doc/}
\newblock Accessed: 2026.

\end{thebibliography}