% ---------------------------------------------------------------
% CHAPTER 1: INTRODUCTION
% ---------------------------------------------------------------
\chapter{Introduction}

IDFC FIRST Bank is pursuing an ambitious strategic vision centered on becoming a 
cutting-edge ``technology-driven'' organization, emphasizing digital transformation 
and robust engineering methodologies to revolutionize consumer banking services. 
To realize this objective, the bank is committed to nurturing a cohort of software 
engineers proficient in designing, developing, and operating production-ready systems 
across all layers --- including distributed microservices infrastructure, high-volume 
data processing systems, user-facing applications, and agile team frameworks.

This document presents findings from an Application Engineer Internship completed at 
\textbf{IDFC FIRST Bank}, conducted across two cities: Hyderabad (January through March 
2026) and Chennai (April through June 2026). The program included pedagogical training 
in engineering fundamentals, a cross-functional collaborative development initiative, 
and an autonomous engineering project tackling a legitimate operational challenge 
within the bank's event-driven service infrastructure.

\section{About IDFC FIRST Bank}

IDFC FIRST Bank was formed in December 2018 following the consolidation of IDFC Bank 
and Capital First Limited. It serves as a contemporary private financial institution 
concentrating on consumer finance and financial accessibility, with global headquarters 
at One World Centre in Mumbai. The organization maintains public listings on both the 
Bombay Stock Exchange (ticker: IDFCFIRSTB) and the National Stock Exchange of India.

\begin{figure}[H]
\centering
\begin{tikzpicture}[node distance=0.45cm]
  \node[rectangle, fill=idfcblue, text=white, minimum width=12.5cm,
        minimum height=0.8cm, font=\bfseries\large, rounded corners=4pt]
    (title) {IDFC FIRST Bank --- Key Facts at a Glance};
  \node[block, below=0.4cm of title, xshift=-3.2cm, text width=5.5cm] (f1)
    {Founded: December 2018};
  \node[block, below=0.4cm of title, xshift= 3.2cm, text width=5.5cm] (f2)
    {Listed: BSE (IDFCFIRSTB) \& NSE};
  \node[block, below=0.4cm of f1, text width=5.5cm] (f3)
    {Employees: 37,000+};
  \node[block, below=0.4cm of f2, text width=5.5cm] (f4)
    {Branches Pan-India: 900+};
  \node[block, below=0.4cm of f3, text width=5.5cm] (f5)
    {Customers: 30 million+};
  \node[block, below=0.4cm of f4, text width=5.5cm] (f6)
    {Total Deposits: Rs.\ 2.3 Lakh Crore+};
  \node[greenblock, below=0.4cm of f5, text width=5.5cm] (f7)
    {Core Focus: Retail Banking \& Financial Inclusion};
  \node[greenblock, below=0.4cm of f6, text width=5.5cm] (f8)
    {HQ: One World Centre, Mumbai};
  \node[wideyellowblock, below=0.9cm of f7, xshift=3.2cm,
        text width=12.2cm] (f9)
    {Philosophy: Customer-First, Transparent \& Digital-First Banking};
\end{tikzpicture}
\caption{IDFC FIRST Bank --- Key Statistics}
\end{figure}

\section{Internship Overview}

\begin{figure}[H]
\centering
\begin{tikzpicture}[node distance=0.45cm]
  \node[rectangle, fill=idfcblue, text=white, minimum width=12.5cm,
        minimum height=0.8cm, font=\bfseries\large, rounded corners=4pt]
    (title) {Internship at a Glance};
  \node[block, below=0.4cm of title, xshift=-3.2cm, text width=5.5cm] (r1)
    {Role: Application Engineer Intern};
  \node[block, below=0.4cm of title, xshift= 3.2cm, text width=5.5cm] (r2)
    {Organisation: IDFC FIRST Bank};
  \node[block, below=0.4cm of r1, text width=5.5cm] (r3)
    {Duration: 27 Jan 2026 --- June 2026};
  \node[block, below=0.4cm of r2, text width=5.5cm] (r4)
    {Department: Web Development};
  \node[block, below=0.4cm of r3, text width=5.5cm] (r5)
    {Location: Hyderabad (Feb--Mar) / Chennai (Apr--Jun)};
\end{tikzpicture}
\caption{Internship Details}
\end{figure}

\section{Motivation}

Present-day financial institutions require software engineering solutions characterized 
by resilience, measurability, and accelerated deployment timelines. Satisfying these 
imperatives demands engineers possessing expertise spanning the entire technology stack --- 
including concurrent backend systems, cross-functional agile team leadership, and resolution 
of platform-level reliability impediments that manifest during live operations. This internship 
initiative was deliberately organized to cultivate precisely this versatility: core competency 
building in Go programming, a comprehensive full-stack project implementation, and a 
self-directed undertaking focused on solving a concrete fault-tolerance vulnerability 
within one of the bank's message-oriented solutions. The assignment scope and technical 
requirements were determined by authentic organizational needs rather than predetermined scope.

\section{Our Contribution}

\begin{figure}[H]
\centering
\begin{tikzpicture}[node distance=0.5cm]
  \node[rectangle, fill=idfcblue, text=white, minimum width=12.5cm,
        minimum height=0.8cm, font=\bfseries, rounded corners=4pt]
    (title) {Three Pillars of Contribution};
  \node[wideblock, below=0.5cm of title, text width=12.2cm,
        minimum height=1cm] (c1)
    {\textbf{Pillar 1 --- DOJO Training:}
      GoLang, concurrency, Gin framework, TDD, Docker};
  \node[widegreenblock, below=0.4cm of c1, text width=12.2cm,
        minimum height=1cm] (c2)
    {\textbf{Pillar 2 --- SkyFox Cinemas:}
      Full-stack Agile project simulation (Tech Lead, 3 sprints, 11-member team)};
  \node[widepurpleblock, below=0.4cm of c2, text width=12.2cm,
        minimum height=1cm] (c3)
    {\textbf{Pillar 3 --- Resilient Event Consumer Framework:}
      Production-grade GoLang library for Kafka fault tolerance
      (87\% coverage, zero event loss)};
\end{tikzpicture}
\caption{Three Pillars of Internship Contribution}
\end{figure}

