\chapter{Conclusions and Future Works}

This internship at Wells Fargo provided practical exposure to enterprise-scale engineering where reliability, governance, and response speed are as important as feature delivery. Through the three workstreams, I contributed to decisioning modernization, cost-aware architecture strategy, and fraud data centralization.

\section{Conclusions}

The major conclusions are as follows:

\begin{itemize}
	\item Automating rule compilation and artifact publication substantially improves consistency and reduces manual operational risk.
	\item Repository consolidation improves maintainability and lowers cognitive overhead for development teams.
	\item In-house stand-in decisioning capability is a viable strategic direction for reducing long-term vendor dependency and improving service continuity.
	\item Event-driven fraud centralization is essential for maintaining a unified risk view across teams and preventing contradictory decisions.
\end{itemize}

Overall, the internship demonstrated that sustainable impact comes from systems thinking: aligning architecture choices with business goals, compliance constraints, and operational realities.

\section{Future Works}

Future scope for this work includes:

\begin{enumerate}
	\item \textbf{Decisioning automation hardening}
	\begin{itemize}
		\item Add rule schema validation and policy quality gates before compilation.
		\item Introduce approval-driven promotion flow across environments.
	\end{itemize}

	\item \textbf{Stand-in server productionization}
	\begin{itemize}
		\item Build parity dashboards comparing internal and third-party outcomes.
		\item Execute phased traffic migration with rollback guardrails.
	\end{itemize}

	\item \textbf{Fraud pipeline resilience}
	\begin{itemize}
		\item Strengthen idempotency controls and event contract governance.
		\item Add dead-letter queue analytics and lag-based alerting.
	\end{itemize}
\end{enumerate}

\section{Personal Learning Outcomes}

\subsection{Technical and Professional Learning}

I learned to translate business pain points into implementable technical architecture, design migration paths with controlled risk, and evaluate solutions through enterprise non-functional requirements such as reliability, traceability, and scalability.

\subsection{Learning to Use GitHub Copilot Better}

During this internship, I improved how I use GitHub Copilot in practical engineering tasks:

\begin{itemize}
	\item I learned to write context-rich prompts so generated code better matches domain requirements.
	\item I used Copilot to accelerate boilerplate, refactoring, and documentation drafting while keeping validation responsibility with myself.
	\item I used iterative prompting to compare alternatives for readability, maintainability, and production safety.
	\item I learned that Copilot is most effective as a productivity partner when paired with strong engineering judgment and testing discipline.
\end{itemize}

These learnings improved both development speed and communication quality during project execution.