\chapter{Methodology}

The internship execution followed an engineering methodology that combined problem decomposition, architecture-first planning, automation-driven implementation, and impact-oriented evaluation.

\section{Workstream Decomposition}

To keep delivery structured and measurable, the complete internship scope was divided into three workstreams:

\begin{enumerate}
	\item Decisioning platform modernization and automation.
	\item In-house stand-in decision server design.
	\item Kafka-based fraud data centralization.
\end{enumerate}

Each workstream had a dedicated problem statement, target outcome, and identified operational constraints.

\section{Requirement Gathering and Validation}

Requirements were interpreted from actual process behavior and stakeholder expectations:

\begin{itemize}
	\item \textbf{Business teams:} faster and reliable policy/rule deployment.
	\item \textbf{Engineering teams:} reduced manual operations and maintainable architecture.
	\item \textbf{Operations and risk teams:} better traceability, resilience, and fraud response speed.
\end{itemize}

Validation was carried out through architecture reviews, implementation feasibility checks, and alignment with production-readiness principles.

\section{Method for Workstream 1: Decisioning Automation}

The approach for the first workstream involved:

\begin{itemize}
	\item Identifying manual steps in the rule-to-artifact lifecycle.
	\item Replacing manual compilation with CI-triggered build execution.
	\item Standardizing artifact naming and versioning for \texttt{.adb} files.
	\item Publishing artifacts to Artifactory for controlled downstream consumption.
\end{itemize}

This method targeted release reliability and auditable deployment flow.

\section{Method for Workstream 2: Stand-in Server Strategy}

The stand-in initiative used a phased methodology:

\begin{itemize}
	\item Define technical stack and service boundaries.
	\item Design APIs and integration points compatible with existing consumers.
	\item Plan fallback-first deployment instead of immediate full replacement.
	\item Use parity and confidence checkpoints before traffic expansion.
\end{itemize}

This methodology reduces migration risk and enables evidence-based adoption.

\section{Method for Workstream 3: Fraud Centralization Pipeline}

The fraud workflow method was event-driven:

\begin{itemize}
	\item Publish incoming fraud-check events via Kafka producers.
	\item Consume events in central services through listeners.
	\item Persist blocked or under-investigation status in a central repository.
	\item Update the same record lifecycle after fraud review outcomes.
\end{itemize}

This method enables multi-team consistency and near real-time state propagation.

\section{Evaluation Framework}

The solutions were evaluated with practical enterprise criteria:

\begin{itemize}
	\item \textbf{Speed:} reduction in manual processing time for rule updates.
	\item \textbf{Reliability:} consistency and repeatability of build and artifact release.
	\item \textbf{Scalability:} ability to support additional producers/consumers and services.
	\item \textbf{Governance:} traceability, version control, and operational audit readiness.
	\item \textbf{Cost impact:} long-term reduction in third-party dependency exposure.
\end{itemize}

\section{Assumptions and Constraints}

The following constraints influenced methodology decisions:

\begin{itemize}
	\item Existing enterprise systems could not be abruptly replaced.
	\item Business approvals were necessary for traffic and policy-impacting changes.
	\item Security, compliance, and reliability requirements had to be preserved throughout.
\end{itemize}

Therefore, incremental rollout and controlled integration were prioritized over disruptive migrations.