\chapter{Results and Discussion}

This chapter summarizes the observed outcomes of the internship initiatives and discusses business relevance, technical implications, and identified limitations.

\section{Results of Decisioning Modernization}

The modernization and automation of decisioning artifacts provided clear operational improvements:

\begin{itemize}
	\item Rule changes became pipeline-driven instead of manually compiled.
	\item Artifact publication became standardized through Artifactory.
	\item Versioning improved traceability and rollback readiness.
	\item Consolidation reduced complexity caused by fragmented repositories.
\end{itemize}

\textbf{Discussion:} The primary gain is not only speed but reliability under repeated releases. In regulated financial systems, consistent and auditable release behavior is as critical as low deployment latency.

\section{Results of Stand-in Server Initiative}

The stand-in server initiative established a practical path toward reducing external dependency.

\begin{itemize}
	\item Internal architecture for fallback decisioning was defined.
	\item Technology stack decisions were aligned with enterprise compatibility.
	\item Phased migration strategy reduced operational risk.
\end{itemize}

\textbf{Discussion:} The largest value is strategic. Even before full replacement, a reliable backup service improves continuity and strengthens operational resilience during third-party outages.

\section{Results of Fraud Centralization Pipeline}

The event-driven fraud architecture produced a structured mechanism for cross-team visibility.

\begin{itemize}
	\item Incoming fraud-check events can be streamed through Kafka.
	\item Consumers update a centralized repository for blocked and investigation states.
	\item Post-investigation updates close the lifecycle loop for consistent status tracking.
\end{itemize}

\textbf{Discussion:} A centralized fraud state reduces risk of contradictory decisions across banking units. This is particularly important in identity theft cases where delayed synchronization can cause severe compliance and financial impact.

\section{Measurable Outcomes Summary}

\begin{table}[h]
	\centering
	\small
	\renewcommand{\arraystretch}{1.35}
	\begin{tabular}{|p{0.17\textwidth}|p{0.17\textwidth}|p{0.21\textwidth}|p{0.21\textwidth}|p{0.17\textwidth}|}
		\hline
		\textbf{Initiative} & \textbf{KPI} & \textbf{Baseline Challenge} & \textbf{Post-Implementation Outcome} & \textbf{Business Impact} \\
		\hline
		Decisioning modernization & Rule release lead time; manual steps per release; artifact traceability rate & Manual rule compile and publish process with fragmented ownership & Push-triggered automated compile and publish path established; versioned \texttt{.adb} artifacts stored in Artifactory & Faster policy rollout and stronger audit readiness \\
		\hline
		Stand-in decision server & Internal decision coverage (\%); third-party dependency ratio; continuity readiness score & High external dependency for cloud/local third-party engines and associated recurring cost & In-house backup architecture defined (Spring Boot + React/TS) with phased adoption strategy and parity-first rollout model & Improved resilience posture and long-term cost optimization path \\
		\hline
		Fraud centralization pipeline & Fraud state propagation latency; cross-team consistency rate; stale-status incidence & No unified repository for blocked/under-investigation transactions & Kafka producer-consumer flow with central repository updates and lifecycle status synchronization implemented & Faster fraud response and reduced contradictory decision risk \\
		\hline
	\end{tabular}
	\caption{Measurable outcomes framework across internship initiatives.}
\end{table}

\textbf{Recommended KPI tracking formulas for deployment dashboards:}

\begin{itemize}
	\item \textbf{Rule Release Lead Time} = \textit{Artifact Published Timestamp} - \textit{Rule Commit Timestamp}
	\item \textbf{Internal Decision Coverage (\%)} = $\frac{\mbox{Requests served by stand-in}}{\mbox{Total decision requests}} \times 100$
	\item \textbf{Fraud Propagation Latency} = \textit{Central Repository Update Timestamp} - \textit{Fraud Event Publish Timestamp}
	\item \textbf{Cross-Team Consistency Rate (\%)} = $\frac{\mbox{Decisions aligned with latest fraud status}}{\mbox{Total evaluated decisions}} \times 100$
\end{itemize}

\section{Limitations and Risks}

Although the outcomes are positive, some limitations remain:

\begin{itemize}
	\item Pipeline reliability must be maintained to avoid build bottlenecks.
	\item Stand-in service requires sustained parity verification against existing engines.
	\item Kafka-based systems require disciplined handling of ordering, retries, and duplicates.
	\item Data governance is critical for sensitive fraud records and lifecycle retention.
\end{itemize}

\section{Key Learnings from Discussion}

The discussion across all workstreams highlights a common pattern: enterprise engineering success depends on combining automation, architecture discipline, and controlled rollout. High-quality software outcomes in banking are created when technical decisions are tied directly to business risk and compliance needs.